---
title: famCHESS EDA
author: Kendra Wyant
editor_options: 
  chunk_output_type: console
---

## Notes

This script reads in the cleaned famCHESS data and performs EDA on final variables.


## Setup

```{r}
options(conflicts.policy = "depends.ok")
suppressMessages(library(tidyverse))
suppressMessages(library(janitor))
theme_set(theme_classic()) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
path_data <- format_path("studydata/famchess")
```


## Data

### Cleaning

```{r}
data <- haven::read_sav(here::here(path_data, "Famchess_clean_combined_FINAL.sav")) |> 
  clean_names() 

dsm <- haven::read_sav(here::here(path_data, "FamCHESS_DSM5.sav")) |> 
  clean_names() # for stratification check
```

Remove participants with inaccurate data (from Olivia's script):  

- 167PT (baseline and 4 month): FAM passed away after baseline
- 208FAM & 208PT (noted on all timepoints): Might be wholly unreliable since we suspect he is his own partner
- 365PT (noted on 1 timepoint): Answered relationship questions about her dog, not her son
- 365FAM (noted on 1 timepoint): Answered relationship questions about romantic partner, not his mom

```{r}
data <- data |> 
  filter(!study_id %in% c("167PT", "208FAM", "208PT", "365PT", "365FAM"))
```

Recode variables (from Olivia's script)     

195PT: reported prefer not to say for gender on baseline but reported male in TLFB data. Changing to male to match TLFB.
```{r}
data <- data |> 
  mutate(gender = if_else(study_id == "195PT", 2, gender))
```


Gender - 2 levels (male / non-male) - TLFB is also coded this way   

- 500PT: non-binary
- 128FAM: Transgender women

*KW: currently setting these two people to Non-male, however, I saw this in scales/measures doc - not enough non-man/ women responses to have 3rd level. For patients, those who don’t fall into groups set to missing*

```{r}
data <- data |> 
  mutate(gender_original = gender, 
         gender = if_else(gender != 2, 1, gender),
         gender = sjlabelled::set_labels(gender, labels = c("Non-male", "Male"))) 

tabyl(data$gender_original)
tabyl(data$gender)
```


Create binary covariate for race/ethnicity defined as: White only (non-Hispanic) vs. not White only   
```{r}
data <- data |> 
  mutate(race_white_only = if_else(ethnicity == 0 & race_1 == 1 &
                                     race_2 == 0 & race_3 == 0 &
                                     race_4 == 0 & race_5 == 0 &
                                     race_6 == 0, 1, 0))

tabyl(data$race_white_only)
```

Center non-binary covariates: age and edu

```{r}
data <- data |> 
  mutate(age_c = age - mean(age, na.rm = TRUE))
```

*KW: education is not continuous. Is centering best transformation? Maybe instead pick a certain level?*
```{r}
sjlabelled::get_labels(data$edu)

mean(data$edu, na.rm = TRUE)

tabyl(data$edu)
```

Recode data to have baseline scores of outcomes as covariate   

*KW: 36 study ids provided baseline info but no data at later time points*
```{r}
baseline_values <- data |>  
  filter(time == 0) |> 
  select(study_id, 
         hdd_0 = per_heavy_drink_days, 
         pda_0 = per_days_abstinent, 
         oq45_0 = oq45_scored, 
         relationsatisf_0 = relationsatisf_scored, 
         abuse_0 = abuse_scored)

baseline_values |> 
  filter(!study_id %in% subset(data, time != 0)$study_id) |> 
  print(n = Inf)
```


```{r}
data <- data |> 
  filter(time != 0) |> 
  full_join(baseline_values, by = "study_id")
```

*KW: confirm this is okay with John - remove 36 individuals with only baseline data*   

*KW: Remove partners too?*

```{r}
dyad_ids <- baseline_values |> 
  mutate(dyad_id = str_sub(study_id, 1, 3)) |> 
  filter(!study_id %in% subset(data, time != 0)$study_id) |> 
  pull(dyad_id) |> 
  unique()
  
data |> 
  mutate(dyad_id = str_sub(study_id, 1, 3)) |> 
  filter(dyad_id %in% dyad_ids) |> 
  select(study_id, dyad_id) |> 
  unique() |> 
  arrange(dyad_id) |> 
  print(n = Inf)

data <- data |> 
  mutate(dyad_id = str_sub(study_id, 1, 3)) |> 
  filter(!dyad_id %in% dyad_ids) |> 
  select(-dyad_id)
```


Center baseline values of outcomes   

```{r}
data <- data |> 
  mutate(hdd_0 = hdd_0 - mean(hdd_0, na.rm = TRUE),
         pda_0 = pda_0 - mean(pda_0, na.rm = TRUE),
         oq45_0 = oq45_0 - mean(oq45_0, na.rm = TRUE),
         relationsatisf_0 = relationsatisf_0 - mean(relationsatisf_0, na.rm = TRUE),
         abuse_0 = abuse_0 - mean(abuse_0, na.rm = TRUE))
```


Center time at the end of the intervention period (8 months).  

```{r}
sjlabelled::get_labels(data$time)

tabyl(data$time)

data <- data |> 
  mutate(time_c = time - 2)
```


Create integer variable for heavy drinking days and days abstinent (baseline and followup values) - needed for negative binomial model
```{r}
data <- data |> 
  mutate(r_hdd = round(per_heavy_drink_days),
         r_hdd_0 = round(hdd_0),
         r_pda = round(per_days_abstinent),
         r_pda_0 = round(pda_0))
```


### EDA

Remove vars not used in analyses (e.g., keep scale score and remove individual items).

*KW: phq, promis, loneliness, coping, interaction scales not scored or in measures doc. Removed from analyses data set.*

```{r}
data <- data |> 
  select(-c(treatmentskills_1:treatmentskills_18_recode,
            oq45_1:oq45_45, alcoholproblems_1:alcoholproblems_15, 
            relationsatisf_1:relationsatisf_8, phq_1:phq_8, 
            abuse_1:abuse_16_yes, promis29_1:promis29_8, 
            abuse_physical_scored:abuse_psychological_scored, gender_open,
            loneliness_1:loneliness_8, healthservice_1, healthservice_2,
            healthservice_3,healthservice_4,healthservice_5, 
            healthservice_5a_1:healthservice_5c, 
            healthservice_6a_1:healthservice_8a, healthservice_8b, 
            healthservice_9a, healthservice_9b, bonding_1:bonding_5, 
            socrates_1:socrates_20, coping_1:coping_25, 
            drinkinggoals:drinkinggoal_7_text, covid_1:covid_3f,
            interaction_1:interaction_20, drink_druguse_1:drinkdruguse_8d,
            abuse_0, employmentstatus:notemployed_open, ethnicity:race_open, 
            livewith_1:livewith_open, meetings_yn, er_yn, outpatient_yn, inpatient_yn,
            n_days, mean_drinks_per_day, per_drink_days, covid_scored,
            redcap_event_name, recruitment_id)) |> 
  rename(other_medications_yn = healthservice_6,
         readmits_yn = r_eadmits_yn) |>  # renaming for descriptive/consistency
  relocate(study_id) |> 
  glimpse()
```


Number of participants
```{r}
data |> 
  pull(study_id) |>
  unique() |> 
  length() # 340

data |> 
  filter(dyad == 1) |> # partner
  pull(study_id) |> 
  unique() |> 
  length()

data |> 
  filter(dyad == 2) |> # patient
  pull(study_id) |> 
  unique() |> 
  length()
```

Complete dyad (patient + partner) for all participants
```{r}
data |> 
  select(study_id) |> 
  unique() |> 
  mutate(dyad_id = str_sub(study_id, 1, 3)) |> 
  group_by(dyad_id) |> 
  count() |> 
  filter(n != 2)
```


Missing data 

```{r}
data |> 
  naniar::miss_var_summary() |> 
  print(n = Inf)
```

Missing data for just patients     

- treatmentskills not applicable to patients
- abuse and readmits have high missing data
- Why days_app_use missing so high? 

```{r}
data |> 
  filter(dyad == 2) |> 
  naniar::miss_var_summary() |> 
  print(n = Inf)
```

Remove `readmits_yn` as covariate due to low endorsement    

*KW: not sure why so many NAs*
```{r}
sjlabelled::get_labels(data$readmits_yn)

data <- data |> 
  select(-readmits_yn)
```



Missing data for partners

```{r}
data |> 
  filter(dyad == 1) |> 
  naniar::miss_var_summary() |> 
  print(n = Inf)
```


Participants in each arm
```{r}
data |> 
  group_by(study_id) |> 
  slice(1) |> 
  tabyl(arm)
```


Check stratification variables in arms - patient gender identity and alcohol use severity (moderate or severe AUD)    

DSM5 criteria: 1 = severe, 2 = moderate, 3 = mild    
Group: 0 = patient control, 1 = patient achess, 2 = patient famchess,  
```{r}
data |> 
  filter(dyad == 2) |> 
  group_by(study_id) |> 
  slice(1) |> 
  tabyl(group, gender)

data |> 
  filter(dyad == 2) |> 
  group_by(study_id) |> 
  slice(1) |> 
  left_join(dsm |> 
              select(study_id, dsm5_criteria), by = "study_id") |> 
  tabyl(group, dsm5_criteria)
```

Demographic and study related variables    

Time string matches time
```{r}
data |> 
  tabyl(time, time_string)
```

*KW: discuss with John if we need to do anything with these notes*
```{r}
data |> 
  filter(!comments == "") |> 
  pull(comments)
```

Income
```{r}
sjlabelled::get_labels(data$income)

tabyl(data$income)
```

Partner relationship
```{r}
sjlabelled::get_labels(data$partner_relationship)

tabyl(data$partner_relationship)
```

Employment
```{r}
sjlabelled::get_labels(data$employment)

tabyl(data$employment)
```

Relationship status with partner
```{r}
sjlabelled::get_labels(data$relationship_status)

tabyl(data$relationship_status)

data |> 
  filter(relationship_status == 4 & relationship_status_open != "") |>
  pull(relationship_status_open)
```

univariate descriptives of covariates, mediators, moderators and outcome variables
```{r}
data |> 
  select(age, edu, days_app_use:r_pda_0, -gender_original, -age_c, 
         -relationship_status, - relationship_status_open, -c(time_c:r_pda_0)) |> 
  skimr::skim()
```

Bivariate correlations for Patient  

*KW: simplify?*    

Notes:   

patient primary outcome = `per_heavy_drink_days`   
partner primary outcome = `oq45_scored`   

patient secondary outcome = `per_days_abstinent`   
partner secondary outcomes = `relationsatisf_scored` and `abuse_scored`    

```{r}
data |> 
  filter(dyad == 2) |> 
  select(age, edu, days_app_use:r_pda_0, -gender_original, -age_c,
         -treatmentskills_scored, -relationship_status, 
         -relationship_status_open, -c(time_c:r_pda_0)) |> 
  cor(use = "pairwise.complete.obs") |> 
  round(2)
```


Look for significant covariates (We will only include covariates that significantly predict the outcome).         

List of covariate variable names: race_white_only, age_c, edu_c, meetings_yn, outpatient_yn_ever, er_yn_ever, mat_yn, inpatient_yn_ever, other_psych_treatment_yn, other_medications_yn   

*KW: COVID acute/residual symptoms was originally listed as covariate but is removed per measures doc (Participants interpreted question differently).*

```{r}

```

Check distribution of residuals

```{r}

```


### Save out processed data for analyses
```{r}
data |> 
  write_csv(here::here(path_data, "famchess_data_ana.csv"))
```

