---
title: famCHESS Modeling EDA
author: Kendra Wyant
editor_options: 
  chunk_output_type: console
---

## Notes

This script reads in the processed famCHESS data (see `eda_cleaning.qmd`) and performs modeling checks for assumptions, covariates, mediators, and moderators.


## Setup

```{r}
options(conflicts.policy = "depends.ok")
suppressMessages(library(tidyverse))
suppressMessages(library(janitor))
library(Matrix, exclude = c("expand", "pack", "unpack"))
library(lme4)
theme_set(theme_classic()) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
path_data <- format_path("studydata/famchess")
```


## Data

```{r}
data <- read_csv(here::here(path_data, "famchess_data_ana.csv"),
                 show_col_types = FALSE) |> 
  mutate(across(where(is.character), ~as.factor(.x))) |> 
  glimpse()
```

Center baseline values of outcomes   
```{r}
data <- data |> 
  mutate(hdd_0 = hdd_0 - mean(hdd_0, na.rm = TRUE),
         pda_0 = pda_0 - mean(pda_0, na.rm = TRUE),
         oq45_0 = oq45_0 - mean(oq45_0, na.rm = TRUE),
         relationsatisf_0 = relationsatisf_0 - mean(relationsatisf_0, na.rm = TRUE),
         abuse_0 = abuse_0 - mean(abuse_0, na.rm = TRUE))
```

Center time at the end of the intervention period (8 months).  
```{r}
data <- data |> 
  mutate(time = factor(time, levels = c("4 Month", "8 Month", "12 Month")),
         time_c = as.numeric(time) - 2)
```

Center non-binary covariates
```{r}
data <- data |> 
  mutate(age_c = age - mean(age, na.rm = TRUE),
         edu = factor(edu, levels = c("8th grade or less", 
                                      "Some high school, but did not graduate",
                                      "High school graduate or GED",
                                      "Some college or 2 year degree",
                                      "4-year college graduate",
                                      "More than 4-year college degree")),
         edu_c = as.numeric(edu) - mean(as.numeric(edu), na.rm = TRUE))
```

### Check Assumptions for Analyses of Study Arm Effects 

patient primary outcome = `per_heavy_drink_days`   
partner primary outcome = `oq45_scored`   

patient secondary outcome = `per_days_abstinent`   
partner secondary outcomes = `relationsatisf_scored` and `abuse_scored`    

*KW: Cannot run primary and secondary patient models for partners (outcomes don't exist). We could run primary and secondary partner models for patients, but does this make sense?*   

List of potential covariate variable names: `race_white_only`, `age_c`, `edu_c`, `meetings_yn`, `outpatient_yn_ever`, `er_yn_ever`, `mat_yn`, `inpatient_yn_ever`, `other_psych_treatment_yn`, `other_medications_yn`      

Set contrasts
```{r}
col_names <- c("fam_and_achess_vs_C", "achess_vs_fam")
arm_contrasts <- matrix(c(1/3, 1/3, -2/3, 1/2, -1/2, 0),
                          nrow = 3, ncol = 2,
                          dimnames = list(levels(data$arm), col_names))

data <- data |> 
  mutate(arm_c = as.factor(arm))

contrasts(data$arm_c) <- arm_contrasts
contrasts(data$arm_c)
```


#### Primary Patient Outcome: `per_heavy_drink_days`

##### Check distribution of residuals

*KW: seems normal enough?*
```{r}
model_patient_prim <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                             (1 + time_c | study_id), 
                           data = subset(data, dyad == "Patient"))

tibble(error = residuals(model_patient_prim)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```


##### Look for significant covariates (We will only include covariates that significantly predict the outcome). 


`race_white_only` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + race_white_only + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("race_white_onlyYes"))
```

`age_c` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + age_c + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + edu_c + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + meetings_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_ynYes"))
```

`outpatient_yn_ever` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + outpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad ==  "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("outpatient_yn_everYes"))
```

`er_yn_ever` - **significant**
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + er_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad ==  "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_everYes"))
```

`mat_yn` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + mat_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_ynYes"))
```

`inpatient_yn_ever` - **significant**
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + inpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad ==  "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("inpatient_yn_everYes"))
```

`other_psych_treatment_yn` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + other_psych_treatment_yn + 
       (1 + time_c | study_id), data = subset(data, dyad ==  "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_psych_treatment_ynYes"))
```

`other_medications_yn` - not significant
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + other_medications_yn + 
       (1 + time_c | study_id), data = subset(data, dyad ==  "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_medications_ynYes"))
```


##### Final Model with Significant Covariates
```{r}
lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + inpatient_yn_ever + 
       er_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad ==  "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F)
```


#### Primary Partner Outcome: `oq45_scored`

Distribution of residuals    
*KW: Looks fine*
```{r}
model_partner_prim <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                             (1 + time_c | study_id), 
                           data = subset(data, dyad == "Partner"))

tibble(error = residuals(model_partner_prim)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)

model_partner_prim_px <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                             (1 + time_c | study_id), 
                           data = subset(data, dyad == "Patient"))

tibble(error = residuals(model_partner_prim_px)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```

##### Look for significant covariates (We will only include covariates that significantly predict the outcome).         
*Checking for sig covariates for partner and patient dyads*

`race_white_only` - not significant
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + race_white_only +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("race_white_onlyYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + race_white_only +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("race_white_onlyYes"))
```

`age_c` - not significant
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + age_c + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + age_c + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - **significant for partner but not patient**
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + edu_c + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + edu_c + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + meetings_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_ynYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + meetings_yn +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_ynYes"))
```

`outpatient_yn_ever` - **significant for partner** Not significant for patient
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + outpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("outpatient_yn_everYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + outpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("outpatient_yn_everYes"))
```

`er_yn_ever` - Not significant
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + er_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_everYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + er_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_everYes"))
```

`mat_yn` - not significant for partner, **significant for patient**
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + mat_yn + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_ynYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + mat_yn + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_ynYes"))
```

`inpatient_yn_ever` - not significant 
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + inpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("inpatient_yn_everYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + inpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("inpatient_yn_everYes"))
```

`other_psych_treatment_yn` - **significant for partner** not significant for patient
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + other_psych_treatment_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_psych_treatment_ynYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + other_psych_treatment_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_psych_treatment_ynYes"))
```

`other_medications_yn` - **significant for partner** not significant for patient
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + other_medications_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_medications_ynYes"))

lmer(oq45_scored ~ time_c*arm_c + oq45_0 + other_medications_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_medications_ynYes"))
```


##### Final Model with Significant Covariates
```{r}
lmer(oq45_scored ~ time_c*arm_c + oq45_0 + edu_c + outpatient_yn_ever + 
       other_psych_treatment_yn + other_medications_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F)


lmer(oq45_scored ~ time_c*arm_c + oq45_0 + mat_yn +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F)
```



#### Secondary Patient Outcome: `per_days_abstinent` 

Distribution of residuals   
*Looks fine*
```{r}
model_patient_sec <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                             (1 + time_c | study_id), 
                          data = subset(data, dyad == "Patient"))

tibble(error = residuals(model_patient_sec)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```


##### Look for significant covariates    

`race_white_only` - not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + race_white_only + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("race_white_onlyYes"))
```

`age_c` - not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + age_c + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + edu_c + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - **significant**
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + meetings_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_ynYes"))
```

`outpatient_yn_ever` - **significant**
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + outpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("outpatient_yn_everYes"))
```

`er_yn_ever` - Not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + er_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_everYes"))
```

`mat_yn` - not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + mat_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |>  
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_ynYes"))
```

`inpatient_yn_ever` - **significant**
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + inpatient_yn_ever + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("inpatient_yn_everYes"))
```

`other_psych_treatment_yn` - not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + other_psych_treatment_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_psych_treatment_ynYes"))
```

`other_medications_yn` - not significant
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + other_medications_yn + 
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_medications_ynYes"))
```

##### Final Model with Significant Covariates
```{r}
lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + outpatient_yn_ever + 
       meetings_yn + inpatient_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F)
```

#### Secondary Partner Outcome 1: `relationsatisf_scored`

Distribution of residuals  
```{r}
model_partner_sec_1 <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                              relationsatisf_0 + (1 + time_c | study_id), 
                            data = subset(data, dyad == "Partner"))

tibble(error = residuals(model_partner_sec_1)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)

model_partner_sec_1_px <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                 relationsatisf_0 + (1 + time_c | study_id), 
                            data = subset(data, dyad == "Patient"))

tibble(error = residuals(model_partner_sec_1_px)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```

##### Look for significant covariates
`race_white_only` - not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + race_white_only +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("race_white_onlyYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + race_white_only +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("race_white_onlyYes"))
```

`age_c` - not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + age_c +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + age_c +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - not significant for partner, **significant for patient** 
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + edu_c +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + edu_c +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + meetings_yn +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_ynYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + meetings_yn +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_ynYes"))
```

`outpatient_yn_ever` - Not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       outpatient_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("outpatient_yn_everYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       outpatient_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("outpatient_yn_everYes"))
```

`er_yn_ever` - Not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + er_yn_ever +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_everYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + er_yn_ever +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_everYes"))
```

`mat_yn` - not significant 
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + mat_yn +
       (1 + time_c | study_id), data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_ynYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + mat_yn +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_ynYes"))
```

`inpatient_yn_ever` - **significant for partner** not significant for patient
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       inpatient_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("inpatient_yn_everYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       inpatient_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("inpatient_yn_everYes"))
```

`other_psych_treatment_yn` - not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       other_psych_treatment_yn + (1 + time_c | study_id),
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_psych_treatment_ynYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       other_psych_treatment_yn + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_psych_treatment_ynYes"))
```

`other_medications_yn` - Not significant
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       other_medications_yn + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_medications_ynYes"))

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       other_medications_yn + (1 + time_c | study_id), 
     data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F, 
                    terms = c("other_medications_ynYes"))
```

##### Final Model with Significant Covariates
```{r}
lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
       inpatient_yn_ever + (1 + time_c | study_id), 
     data = subset(data, dyad == "Partner")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F)

lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + edu_c +
       (1 + time_c | study_id), data = subset(data, dyad == "Patient")) |> 
  sjPlot::tab_model(show.re.var = F, show.icc = F)
```


#### Secondary Partner Outcome 2: `abuse_scored`

<!-- Distribution of residuals     -->
<!-- *KW: Look into potential outliers?* -->

<!-- *This model can only be fit for partners? Look into error* -->
<!-- ```{r} -->
<!-- model_partner_sec_2 <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + -->
<!--                              (1 + time_c | study_id),  -->
<!--                             data = subset(data, dyad == "Partner")) -->

<!-- tibble(error = residuals(model_partner_sec_2)) |>  -->
<!--   ggplot(aes(x = error)) + -->
<!--   geom_histogram(color = "black", fill = "light grey", bins = 30) -->
<!-- ``` -->


<!-- ##### Look for significant covariates -->
<!-- `race_white_only` - not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + race_white_only +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("race_white_only")) -->
<!-- ``` -->

<!-- `age_c` - not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + age_c + (1 + time_c | study_id),  -->
<!--      data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("age_c")) -->
<!-- ``` -->

<!-- `edu_c` - Not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + edu_c + (1 + time_c | study_id),  -->
<!--      data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("edu_c")) -->
<!-- ``` -->

<!-- `meetings_yn` - not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + meetings_yn +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("meetings_yn")) -->
<!-- ``` -->

<!-- `outpatient_yn_ever` - Not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + outpatient_yn_ever +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever")) -->
<!-- ``` -->

<!-- `er_yn_ever` - Not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + er_yn_ever +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("er_yn_ever")) -->
<!-- ``` -->

<!-- `mat_yn` - **significant for partner** -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + mat_yn + (1 + time_c | study_id),  -->
<!--      data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("mat_yn")) -->
<!-- ``` -->

<!-- `inpatient_yn_ever` - **significant for partner** -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + inpatient_yn_ever +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever")) -->
<!-- ``` -->

<!-- `other_psych_treatment_yn` - not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + other_psych_treatment_yn +  -->
<!--        (1 + time_c | study_id),  data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn")) -->
<!-- ``` -->

<!-- `other_medications_yn` - Not significant -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + other_medications_yn +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(show.re.var = F, show.icc = F, terms = c("other_medications_yn")) -->
<!-- ``` -->

<!-- ##### Final Model with Significant Covariates -->
<!-- ```{r} -->
<!-- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + mat_yn + inpatient_yn_ever +  -->
<!--        (1 + time_c | study_id), data = subset(data, dyad == 1)) |>  -->
<!--   sjPlot::tab_model(model_partner_sec_2, show.re.var = F, show.icc = F) -->
<!-- ``` -->



### Check Assumptions for Analyses of Mediators

**KW: mediators only for primary outcomes and ACHESS vs. FamCHESS contrasts**   

List of Patient mediators: `socrates_scored`    
List of Partner mediators: `peersupport_scored`, `treatmentskills_scored`

### Check Assumptions for Analyses of Moderators 

**KW: moderators only for primary outcomes**   

List of Patient moderators: `dsm5_criteria`    
List of Partner moderators: `gender`, `days_app_use`
