---
title: famCHESS Modeling EDA
author: Kendra Wyant
editor_options: 
  chunk_output_type: console
---

## Notes

This script reads in the processed famCHESS data (see `eda_cleaning.qmd`) and performs modeling checks for assumptions, covariates, mediators, and moderators.


## Setup

```{r}
options(conflicts.policy = "depends.ok")
suppressMessages(library(tidyverse))
suppressMessages(library(janitor))
library(Matrix, exclude = c("expand", "pack", "unpack"))
library(lme4)
theme_set(theme_classic()) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
path_data <- format_path("studydata/famchess")
```


## Data

```{r}
data <- read_csv(here::here(path_data, "famchess_data_ana.csv"),
                 show_col_types = FALSE)
```


### Check Assumptions for Analyses of Study Arm Effects 

patient primary outcome = `per_heavy_drink_days`   
partner primary outcome = `oq45_scored`   

patient secondary outcome = `per_days_abstinent`   
partner secondary outcomes = `relationsatisf_scored` and `abuse_scored`    

*KW: Cannot run primary and secondary patient models for partners (outcomes don't exist). We could run primary and secondary partner models for patients, but why would we want to do this?*   

List of potential covariate variable names: `race_white_only`, `age_c`, `edu_c`, `meetings_yn`, `outpatient_yn_ever`, `er_yn_ever`, `mat_yn`, `inpatient_yn_ever`, `other_psych_treatment_yn`, `other_medications_yn`      

Set contrasts
```{r}
col_names <- c("fam_and_achess_vs_C", "achess_vs_fam")
arm_contrasts <- matrix(c(-2/3, 1/3, 1/3, 0, 1/2, -1/2),
                          nrow = 3, ncol = 2,
                          dimnames = list(levels(data$arm), col_names))

data <- data |> 
  mutate(arm_c = as.factor(arm))

contrasts(data$arm_c) <- arm_contrasts
contrasts(data$arm_c)
```


#### Primary Patient Outcome: `per_heavy_drink_days`

##### Check distribution of residuals

*KW: seems normal enough?*
```{r}
model_patient_prim <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                             (1 + time_c | study_id), data = subset(data, dyad == 2))

tibble(error = residuals(model_patient_prim)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```


##### Look for significant covariates (We will only include covariates that significantly predict the outcome).         

`race_white_only` - not significant
```{r}
model_patient_prim_race <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                  race_white_only + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))
```

`age_c` - not significant
```{r}
model_patient_prim_age <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                  age_c + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_age, show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - not significant
```{r}
model_patient_prim_edu <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                  edu_c + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
model_patient_prim_meetings <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                  meetings_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))
```

`outpatient_yn_ever` - not significant
```{r}
model_patient_prim_outpatient <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                  outpatient_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))
```

`er_yn_ever` - **significant**
```{r}
model_patient_prim_er <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                er_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))
```

`mat_yn` - not significant
```{r}
model_patient_prim_mat <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                mat_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))
```

`inpatient_yn_ever` - **significant**
```{r}
model_patient_prim_inpatient <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                inpatient_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))
```

`other_psych_treatment_yn` - not significant
```{r}
model_patient_prim_psych <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                other_psych_treatment_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))
```

`other_medications_yn` - not significant
```{r}
model_patient_prim_psych_meds <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                                other_medications_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))
```


##### Final Model with Significant Covariates
```{r}
model_patient_prim <- lmer(per_heavy_drink_days ~ time_c*arm_c + hdd_0 + 
                             inpatient_yn_ever + er_yn_ever +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_prim, show.re.var = F, show.icc = F)
```


#### Primary Partner Outcome: `oq45_scored`

Distribution of residuals    
*KW: Looks fine*
```{r}
model_partner_prim <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                             (1 + time_c | study_id), data = subset(data, dyad == 1))

tibble(error = residuals(model_partner_prim)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```

##### Look for significant covariates (We will only include covariates that significantly predict the outcome).         

`race_white_only` - not significant
```{r}
model_partner_prim_race <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + race_white_only +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))

model_partner_prim_race <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + race_white_only +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))
```

`age_c` - not significant
```{r}
model_partner_prim_age <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + age_c +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_age, show.re.var = F, show.icc = F, terms = c("age_c"))

model_partner_prim_age <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + age_c +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_age, show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - **significant for partner but not patient**
```{r}
model_partner_prim_edu <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + edu_c +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))

model_partner_prim_edu <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + edu_c +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
model_partner_prim_meetings <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + meetings_yn +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))

model_partner_prim_meetings <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + meetings_yn +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))
```

`outpatient_yn_ever` - **significant for partner but not patient**
```{r}
model_partner_prim_outpatient <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                                       outpatient_yn_ever + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))

model_partner_prim_outpatient <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                                       outpatient_yn_ever + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))
```

`er_yn_ever` - Not significant
```{r}
model_partner_prim_er <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              er_yn_ever + (1 + time_c | study_id), 
                          data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))

model_partner_prim_er <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              er_yn_ever + (1 + time_c | study_id), 
                          data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))
```

`mat_yn` - not significant for partner, **significant for patient**
```{r}
model_partner_prim_mat <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              mat_yn + (1 + time_c | study_id), 
                          data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))

model_partner_prim_mat <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              mat_yn + (1 + time_c | study_id), 
                          data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))
```

`inpatient_yn_ever` - not significant 
```{r}
model_partner_prim_inpatient <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              inpatient_yn_ever + (1 + time_c | study_id), 
                          data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))

model_partner_prim_inpatient <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              inpatient_yn_ever + (1 + time_c | study_id), 
                          data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))
```

`other_psych_treatment_yn` - **significant for partner, but not for patient**
```{r}
model_partner_prim_psych <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              other_psych_treatment_yn + (1 + time_c | study_id), 
                          data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))

model_partner_prim_psych <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              other_psych_treatment_yn + (1 + time_c | study_id), 
                          data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))
```

`other_medications_yn` - **significant for partner but not for patient**
```{r}
model_partner_prim_psych_meds <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              other_medications_yn + (1 + time_c | study_id), 
                          data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))

model_partner_prim_psych_meds <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + 
                              other_medications_yn + (1 + time_c | study_id), 
                          data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))
```


##### Final Model with Significant Covariates
```{r}
model_partner_prim <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + edu_c +
                             outpatient_yn_ever + other_psych_treatment_yn +
                             other_medications_yn +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_prim, show.re.var = F, show.icc = F)


model_partner_prim <- lmer(oq45_scored ~ time_c*arm_c + oq45_0 + mat_yn +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_prim, show.re.var = F, show.icc = F)
```



#### Secondary Patient Outcome: `per_days_abstinent` 

Distribution of residuals   
*Looks fine*
```{r}
model_patient_sec <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                             (1 + time_c | study_id), data = subset(data, dyad == 2))

tibble(error = residuals(model_patient_sec)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```


##### Look for significant covariates    

`race_white_only` - not significant
```{r}
model_patient_sec_race <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  race_white_only + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))
```

`age_c` - not significant
```{r}
model_patient_sec_age <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  age_c + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_age, show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - not significant
```{r}
model_patient_sec_edu <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  edu_c + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - **significant**
```{r}
model_patient_sec_meetings <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  meetings_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))
```

`outpatient_yn_ever` - **significant**
```{r}
model_patient_sec_outpatient <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  outpatient_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))
```

`er_yn_ever` - Not significant
```{r}
model_patient_sec_er <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  er_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))
```

`mat_yn` - not significant
```{r}
model_patient_sec_mat <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  mat_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))
```

`inpatient_yn_ever` - **significant**
```{r}
model_patient_sec_inpatient <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  inpatient_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))
```

`other_psych_treatment_yn` - not significant
```{r}
model_patient_sec_psych <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  other_psych_treatment_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))
```

`other_medications_yn` - not significant
```{r}
model_patient_sec_psych_meds <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 + 
                                  other_medications_yn + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))

sjPlot::tab_model(model_patient_sec_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))
```

##### Final Model with Significant Covariates
```{r}
model_patient_sec <- lmer(per_days_abstinent ~ time_c*arm_c + pda_0 +
                            outpatient_yn_ever + meetings_yn +
                            inpatient_yn_ever + (1 + time_c | study_id), 
                                data = subset(data, dyad == 2))
sjPlot::tab_model(model_patient_sec, show.re.var = F, show.icc = F)
```

#### Secondary Partner Outcome 1: `relationsatisf_scored`

Distribution of residuals  
```{r}
model_partner_sec_1 <- lmer(relationsatisf_scored ~ time_c*arm_c + relationsatisf_0 + 
                             (1 + time_c | study_id), data = subset(data, dyad == 1))

tibble(error = residuals(model_partner_sec_1)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```

##### Look for significant covariates
`race_white_only` - not significant
```{r}
model_partner_sec_1_race <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + race_white_only +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))

model_partner_sec_1_race <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + race_white_only +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))
```

`age_c` - not significant
```{r}
model_partner_sec_1_age <-  lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + age_c +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_age, show.re.var = F, show.icc = F, terms = c("age_c"))

model_partner_sec_1_age <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + age_c +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_age, show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - **significant for patient but not partner**
```{r}
model_partner_sec_1_edu <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + edu_c +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))

model_partner_sec_1_edu <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + edu_c +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
model_partner_sec_1_meetings <-lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + meetings_yn +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))

model_partner_sec_1_meetings <-lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + meetings_yn +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))
```

`outpatient_yn_ever` - Not significant
```{r}
model_partner_sec_1_outpatient <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + outpatient_yn_ever +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))

model_partner_sec_1_outpatient <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + outpatient_yn_ever +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))
```

`er_yn_ever` - Not significant
```{r}
model_partner_sec_1_er <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + er_yn_ever +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))

model_partner_sec_1_er <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + er_yn_ever +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))
```

`mat_yn` - not significant 
```{r}
model_partner_sec_1_mat <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + mat_yn +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))

model_partner_sec_1_mat <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + mat_yn +
                             (1 + time_c | study_id), data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))
```

`inpatient_yn_ever` - **significant for partner not patient**
```{r}
model_partner_sec_1_inpatient <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + inpatient_yn_ever +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))

model_partner_sec_1_inpatient <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + inpatient_yn_ever +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))
```

`other_psych_treatment_yn` - not significant
```{r}
model_partner_sec_1_psych <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + other_psych_treatment_yn +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))

model_partner_sec_1_psych <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + other_psych_treatment_yn +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))
```

`other_medications_yn` - Not significant
```{r}
model_partner_sec_1_psych_meds <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + other_medications_yn +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))

model_partner_sec_1_psych_meds <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + other_medications_yn +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))
```

##### Final Model with Significant Covariates
```{r}
model_partner_sec_1 <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + inpatient_yn_ever +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_1, show.re.var = F, show.icc = F)

model_partner_sec_1 <- lmer(relationsatisf_scored ~ time_c*arm_c + 
                                   relationsatisf_0 + edu_c +
                             (1 + time_c | study_id), 
                             data = subset(data, dyad == 2))
sjPlot::tab_model(model_partner_sec_1, show.re.var = F, show.icc = F)
```


#### Secondary Partner Outcome 2: `abuse_scored`

Distribution of residuals    
*KW: Look into potential outliers?*

*This model can only be fit for partners? Look into error*
```{r}
model_partner_sec_2 <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                             (1 + time_c | study_id), data = subset(data, dyad == 1))

tibble(error = residuals(model_partner_sec_2)) |> 
  ggplot(aes(x = error)) +
  geom_histogram(color = "black", fill = "light grey", bins = 30)
```


##### Look for significant covariates
`race_white_only` - not significant
```{r}
model_partner_sec_2_race <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   race_white_only + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_race, show.re.var = F, show.icc = F, terms = c("race_white_only"))
```

`age_c` - not significant
```{r}
model_partner_sec_2_age <-  lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   age_c + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_age, show.re.var = F, show.icc = F, terms = c("age_c"))
```

`edu_c` - Not significant
```{r}
model_partner_sec_2_edu <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   edu_c + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_edu, show.re.var = F, show.icc = F, terms = c("edu_c"))
```

`meetings_yn` - not significant
```{r}
model_partner_sec_2_meetings <-lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   meetings_yn + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_meetings, show.re.var = F, show.icc = F, terms = c("meetings_yn"))
```

`outpatient_yn_ever` - Not significant
```{r}
model_partner_sec_2_outpatient <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   outpatient_yn_ever + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_outpatient, show.re.var = F, show.icc = F, terms = c("outpatient_yn_ever"))
```

`er_yn_ever` - Not significant
```{r}
model_partner_sec_2_er <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   er_yn_ever + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_er, show.re.var = F, show.icc = F, terms = c("er_yn_ever"))
```

`mat_yn` - **significant for partner**
```{r}
model_partner_sec_2_mat <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   mat_yn + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_mat, show.re.var = F, show.icc = F, terms = c("mat_yn"))
```

`inpatient_yn_ever` - **significant for partner**
```{r}
model_partner_sec_2_inpatient <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   inpatient_yn_ever + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_inpatient, show.re.var = F, show.icc = F, terms = c("inpatient_yn_ever"))
```

`other_psych_treatment_yn` - not significant
```{r}
model_partner_sec_2_psych <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   other_psych_treatment_yn + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_psych, show.re.var = F, show.icc = F, terms = c("other_psych_treatment_yn"))
```

`other_medications_yn` - Not significant
```{r}
model_partner_sec_2_psych_meds <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 +
                                   other_medications_yn + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2_psych_meds, show.re.var = F, show.icc = F, terms = c("other_medications_yn"))
```

##### Final Model with Significant Covariates
```{r}
model_partner_sec_2 <- lmer(abuse_scored ~ time_c*arm_c + abuse_0 + mat_yn +
                                   inpatient_yn_ever + (1 + time_c | study_id), 
                                 data = subset(data, dyad == 1))
sjPlot::tab_model(model_partner_sec_2, show.re.var = F, show.icc = F)
```



### Check Assumptions for Analyses of Mediators

**KW: mediators only for primary outcomes and ACHESS vs. FamCHESS contrasts**   

List of Patient mediators: `socrates_scored`    
List of Partner mediators: `peersupport_scored`, `treatmentskills_scored`

### Check Assumptions for Analyses of Moderators 

**KW: moderators only for primary outcomes**   

List of Patient moderators: `dsm5_criteria`    
List of Partner moderators: `gender`, `days_app_use`
